Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-04-26 article/article.tex
(-) spelling mistakes, (~) title

\title{Airspace configuration decision based on Monte-Carlo tree search}
\author{Gabriel~Hondet, Beno\^{\i}t Viry}
\date{\today}
\pagestyle{headings}

@@

The sequence of configurations is represented as a tree. The resulting
sequence will therefore be a path from the root to a leaf of this tree. This
problem is highly combinatorial (partitioning of the airspace). Since stochastic
tree search algorithms, combined with deep neural networks have proved
themselves worthy by outranking the best human player of one of the most highly
combinatorial game which is the game of Go, the Monte Carlo tree
search~\cite{browne2012survey} algorithm is used in this paper to fullfill the
previously mentioned task.

@@

In this paper, each partition scheme is based upon the number of aircraft in
each
elementary module and the cost of transition from the previous partitioning. The
available partitions come from a predetermined set containing feasible
partitionings.

@@

The above mentioned steps are denoted
\begin{compactenum}
\item selection (or tree walk): choosing successively most promising nodes,
\item expansion: adding new nodes to the search tree,
\item simulation (or random walk): choosing successively nodes from the model
  tree,
\item backpropagation (or backup): applying the result of the simulation to
  the search tree.
\end{compactenum}
Those phases are repeated until a stopping criterium (e.g.\ memory or time) is
reached, resulting in algorithm~\ref{alg:gen_mcts} where the tree policy
aggregates phases 1 and 2 to create a new node of the search tree and the
default policy gives an evaluation of the newly added node.
\begin{algorithm}
  \caption{General MCTS~\cite{browne2012survey}}\label{alg:gen_mcts}
  \begin{algorithmic}
    \Procedure{MctsSearchTree}{$v_0$}
    \While{within computational budget}
    \State{}\(\pi \gets\) \Call{TreePolicy}{$v_0$}
    \State{}\(v \gets \first(\pi)\)
    \State{}\(\Delta \gets\) \Call{DefaultPolicy}{$v$}
    \State{}\Call{Backup}{$\pi$, $\Delta$}
    \EndWhile{}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

@@

\subparagraph{Exploration exploitation tradeoff} The constant \(\beta\) answers
to the exploration v exploitation dilemma. In the UCB1 equation~\ref{eq:ucb1},
the left hand term increases the value of less explorated nodes to consider them
as still promising. A high \(\beta\) value will therefore make the algorithm
prone to try unvisited nodes while a low value will consider almost exclusively
the results obtained so far, even if other paths are better.

>>>>

\title{Monte Carlo tree search compared to A\(^*\) in airspace configuration
decision problem}
\author{Gabriel~Hondet, Beno\^{\i}t Viry}
\date{\today}
\pagestyle{headings}

@@

The sequence of configurations is represented as a tree. The resulting
sequence will therefore be a path from the root to a leaf of this tree. This
problem is highly combinatorial (partitioning of the airspace). Since stochastic
tree search algorithms, combined with deep neural networks have proved
themselves worthy by outranking the best human player of one of the most highly
combinatorial game which is the game of Go, the Monte Carlo tree
search~\cite{browne2012survey} algorithm is used in this paper to fulfill the
previously mentioned task.

@@

In this paper, each partition scheme is based upon the number of aircraft in
each
elementary module and the cost of transition from the previous partitioning. The
available partitions come from a predetermined set containing feasible
partitioning.

@@

The above mentioned steps are denoted
\begin{compactenum}
\item selection (or tree walk): choosing successively most promising nodes,
\item expansion: adding new nodes to the search tree,
\item simulation (or random walk): choosing successively nodes from the model
  tree,
\item backpropagation (or backup): applying the result of the simulation to
  the search tree.
\end{compactenum}
Those phases are repeated until a stopping criterion (e.g.\ memory or time) is
reached, resulting in algorithm~\ref{alg:gen_mcts} where the tree policy
aggregates phases 1 and 2 to create a new node of the search tree and the
default policy gives an evaluation of the newly added node.
\begin{algorithm}
  \caption{General MCTS~\cite{browne2012survey}}\label{alg:gen_mcts}
  \begin{algorithmic}
    \Procedure{MctsSearchTree}{$v_0$}
    \While{within computational budget}
    \State{}\(\pi \gets\) \Call{TreePolicy}{$v_0$}
    \State{}\(v \gets \first(\pi)\)
    \State{}\(\Delta \gets\) \Call{DefaultPolicy}{$v$}
    \State{}\Call{Backup}{$\pi$, $\Delta$}
    \EndWhile{}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

@@

\subparagraph{Exploration exploitation trade-off} The constant \(\beta\) answers
to the exploration v exploitation dilemma. In the UCB1 equation~\ref{eq:ucb1},
the left hand term increases the value of less explored nodes to consider them
as still promising. A high \(\beta\) value will therefore make the algorithm
prone to try unvisited nodes while a low value will consider almost exclusively
the results obtained so far, even if other paths are better.
